### 2021-07-31 paper/localpsf.tex
boundary extension written okish

While $\varphi_{x_i}$ may be undefined at a point $z$, often there is a sample point $x_j$ that is near $x_i$, but further away from the boundary than $x_i$, such that $\varphi_{x_j}$ is well defined at $z$. To address boundary artifacts, we fill in missing/undefined portions of convolution kernels using information from other convolution kernels associated with the $k$ nearest sample points. Kernels associated with nearer sample points are given precedence over kernels associated with farther away sample points. After the convolution kernel has been extended using information from neighboring convolution kernels, it is then further extended by zero.

In detail, let $x_{n_1}, x_{n_2}, \dots, x_{n_k}$ be the $k$ nearest sample points to $x_i$, ordered by nearness, including $x_i$ itself. That is, $x_{n_1}=x_i$ (the point itself), $x_{n_2}$ is the nearest sample point to $x_i$ other than $x_i$ itself, $x_{n_3}$ is the second nearest sample point to $x_i$ other than $x_i$ itself, and so on. Also, recall that in computations that the functions $\varphi_{x_i}$ are stored on regular rectilinear grids. To extend $\varphi_{x_i}$, first we form an expanded regular rectilinear grid that has the same grid spacing as the grid used for $\varphi_{x_i}$, and contains that grid as a subgrid, but is large enough to contain the boxes associated with all of the neighbor kernels $\varphi_{x_{n_1}}, \varphi_{x_{n_2}}, \dots, \varphi_{x_{n_k}}$. We initialize an extended convolution kernel, $\varphi_{x_i}^E$, to zero on this expanded grid. Then we interpolate the functions $\varphi_{x_{n_j}}$ onto this expanded grid one at a time in reverse order. That is, first we interpolate the $\varphi_{x_{n_k}}$ onto the grid, then the kernel $\varphi_{x_{n_{k-1}}}$, and so on until we reach the original kernel $\varphi_{x_{n_1}} = \varphi_{x_i}$. At each step, we overwrite existing values of $\varphi_{x_i}^E$ with new values from the kernel currently being interpolated, except when the new value of $\varphi_{x_{n_j}}$ is undefined (``NaN''). At gridpoints where the kernel being interpolated is undefined, we leave $\varphi_{x_i}^E$ unchanged. In this way, we fill in undefined values of $\varphi_{x_i}$ with values from successively further and further away kernels. This process is illustrated in Figure FIG. To avoid notational clutter, and since we will henceforth only work with the extended kernel, $\varphi_{x_i}^E$, in the remainder of this paper the symbol $\varphi_{x_i}$ refers to $\varphi_{x_i}^E$.

>>>>

While $\varphi_{x_i}$ may be undefined at a point $z$, often there is a sample point $x_j$ that is near $x_i$, but further away from the boundary than $x_i$, such that $\varphi_{x_j}$ is well defined at $z$. To address boundary artifacts, we fill in missing/undefined portions of convolution kernels using information from other convolution kernels associated with the $k$ nearest sample points. Kernels associated with nearer sample points are given precedence over kernels associated with farther away sample points. 
%After the convolution kernel has been extended using information from neighboring convolution kernels, it is then further extended by zero.

In detail, let $x_{n_1}, x_{n_2}, \dots, x_{n_k}$ be the $k$ nearest sample points to $x_i$, ordered by nearness, including $x_i$ itself. That is, $x_{n_1}=x_i$ (the point itself), $x_{n_2}$ is the nearest sample point to $x_i$ other than $x_i$ itself, $x_{n_3}$ is the second nearest sample point to $x_i$ other than $x_i$ itself, and so on. Also, recall that in computations that the functions $\varphi_{x_i}$ are stored on regular rectilinear grids. To extend $\varphi_{x_i}$, first we form an expanded regular rectilinear grid that has the same grid spacing as the grid used for $\varphi_{x_i}$, and contains that grid as a subgrid, but is large enough to contain the boxes associated with all of the neighbor kernels $\varphi_{x_{n_1}}, \varphi_{x_{n_2}}, \dots, \varphi_{x_{n_k}}$. We initialize an extended convolution kernel, $\varphi_{x_i}^E$, to zero on this expanded grid. Then we interpolate the functions $\varphi_{x_{n_j}}$ onto this expanded grid one at a time in reverse order. That is, first we interpolate $\varphi_{x_{n_k}}$ onto the grid, then $\varphi_{x_{n_{k-1}}}$, and so on until we reach the original kernel $\varphi_{x_{n_1}} = \varphi_{x_i}$. At each step, we overwrite existing values of $\varphi_{x_i}^E$ with new values from the kernel currently being interpolated, except when the new value of $\varphi_{x_{n_j}}$ is undefined (``NaN''). At gridpoints where the kernel being interpolated is undefined, we leave $\varphi_{x_i}^E$ unchanged. In this way, we fill in undefined values of $\varphi_{x_i}$ with values from successively further and further away kernels. This process is illustrated in Figure FIG. To avoid notational clutter, and since we will henceforth only work with the extended kernel, $\varphi_{x_i}^E$, in the remainder of this paper the symbol $\varphi_{x_i}$ refers to $\varphi_{x_i}^E$.
